|

### 2023-02-13 paper_comparison/paper_comparison/paper_comparison.Rmd
fix effect size issue

        # Get the effect size from the pre-calculated table 
        es <- filter(vi_survey, 
                     shape == {{shape}},
                     e_sigma == {{e_sigma}},
                     x_dist == {{x_dist}},
                     n == {{n}}) %>%
          head(1) %>%
          pull(effect_size)

@@

        # Get the effect size from the pre-calculated table 
        es <- filter(vi_survey, 
                     a == {{a}}, 
                     b == {{b}},
                     x_dist == {{x_dist}},
                     n == {{n}}) %>%
          head(1) %>%
          pull(effect_size)

@@

@@

```{=tex}
\begin{equation} \label{eq:logistic-regression-1-1}
Pr(\text{reject}~H_0|H_1,E) = \Lambda(log(\frac{0.5}{0.95}) + \beta_1 E),
\end{equation}
```
\noindent where $\Lambda(.)$ is the standard logistic function given as $\Lambda(z) = exp(z)/(1+exp(z))$. The effect size is the only regressor and the intercept is fixed to $log(0.5/0.95)$ so that $\hat{Pr}(\text{reject}~H_0|H_1,E = 0) = 0.05$.

@@

```{r cache = TRUE}
# target_sigma is obtained by evaluating a vector of sigma and picking those 
# with expected effect 0 ~ 5
target_sigma <- c(4.51, 3.52, 2.74, 2.14, 1.66, 1.29, 1.01, 0.79, 0.61, 0.48, 0.37)

# Calculate the effect size 
es <- map_dbl(target_sigma, 
              ~log(poly_model(shape = 2, 
                              x = rand_uniform(-1, 1), 
                              sigma = .x)$
                     effect_size(n = 100)
                   )
              )
```

@@

# Base data
ex_dat <- poly_model(shape = 2, 
                     x = rand_uniform(), 
                     sigma = 1)$gen(n = 100)
plist <- list()
j <- 0

@@

# The glm model for visual test
visual_heter_glmmod <- glm(reject ~ effect_size - 1, 
                           family = binomial(), 
                           data = visual_poly_dat, 
                           offset = offset0)

@@

```{r cache = TRUE}
# target_b is obtained by evaluating a vector of b and picking those 
# with expected effect 0 ~ 5
target_b <- c(0.14, 0.19, 0.27, 0.38, 0.57, 0.91, 1.53, 2.9, 6.4, 17.9, 75)

# Calculate the effect size 
es <- map_dbl(target_b, 
              ~log(heter_model(a = 1, 
                               b = .x, 
                               x = rand_uniform(-1, 1))$
                     effect_size(n = 100, type = "kl")
                   )
              )
```

@@

>>>>

        # Get the effect size from the pre-calculated table 
        es <- filter(vi_survey, 
                     shape == {{shape}},
                     e_sigma == {{e_sigma}},
                     n == {{n}}) %>%
          head(1) %>%
          pull(effect_size)

@@

        # Get the effect size from the pre-calculated table 
        es <- filter(vi_survey, 
                     a == {{a}}, 
                     b == {{b}},
                     n == {{n}}) %>%
          head(1) %>%
          pull(effect_size)

@@

(use uniform effect size? normal effect size? -> other dist?)

(average out dist for effect size calc?)

@@

```{=tex}
\begin{equation} \label{eq:logistic-regression-1-1}
Pr(\text{reject}~H_0|H_1,E) = \Lambda(log(\frac{0.05}{0.95}) + \beta_1 E),
\end{equation}
```
\noindent where $\Lambda(.)$ is the standard logistic function given as $\Lambda(z) = exp(z)/(1+exp(z))$. The effect size is the only regressor and the intercept is fixed to $log(0.5/0.95)$ so that $\hat{Pr}(\text{reject}~H_0|H_1,E = 0) = 0.05$.

@@

```{r cache = TRUE}
# target_sigma is obtained by evaluating a vector of sigma and picking those 
# with expected effect 0 ~ 5

target_sigma <- c(3.65, 2.84, 2.21, 1.72, 1.34, 1.04, 0.81, 0.63, 0.49, 0.38, 0.3)

# Calculate the effect size 
es <- map_dbl(target_sigma, 
              ~log(poly_model(shape = 2, 
                              x = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))}, 
                              sigma = .x)$
                     average_effect_size(n = 100)
                   )
              )
```

@@

# Base data
ex_dat <- poly_model(shape = 2, 
                     x = rand_uniform(-1, 1), 
                     sigma = 1)$gen(n = 100)
plist <- list()
j <- 0

@@

# The glm model for visual test
visual_heter_glmmod <- glm(reject ~ effect_size - 1, 
                           family = binomial(), 
                           data = visual_heter_dat, 
                           offset = offset0)

@@

```{r cache = TRUE}
# target_b is obtained by evaluating a vector of b and picking those 
# with expected effect 0 ~ 5

target_b <- c(0.17, 0.23, 0.32, 0.46, 0.67, 1.04, 1.7, 3, 6.3, 16.2, 61)

# Calculate the effect size 
es <- map_dbl(target_b, 
              ~log(heter_model(a = 1, 
                               b = .x, 
                               x = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))})$
                     average_effect_size(n = 100, type = "kl")
                   )
              )
```

@@

(change the butterfly color)
